Boundary terms in the action for Causal Sets

### 2014-10-22 paper_v7.tex
minor corrections in 3.2 mostly in the intro of RNCs

This is now a simple volume integral but we need to find the boundaries of $\mathcal{X}_p$ to write down the integration limits. There are two parts to the boundary of the (solid) truncated cone: the \emph{base}, defined as $B_p:=\Sigma\cap J^-(p)$, and the \emph{top} defined as the set corresponding to the lightcone emanating at $p$ with all points below $\Sigma$ removed, written as $T_p:=\partial J^-(p)\cap J^+(\Sigma)$. Now the boundary of $\mathcal{X}_p$ is simply $\partial\mathcal{X}_p=B_p\cup T_p$. First we look at the top. Following \cite{Khetrapal_Sumati:Causal_Diamond_Volume} it can be shown that the first curvature correction to the lightcone volume comes in at $O (T^{d+2})$ and so can be ignored for our purposes. This means that the top can be treated effectively as a flat lightcone in RNCs, emanating from the point on the time axis at coordinate $T$, and thus it corresponds to the set of points satisfying $ (y^{\overline{1}})^2+ (y^{\overline{2}})^2+...+ (y^{\overline{d-1}})^2= T-\overline{t}$ where the coordinates  $y^{\overline{i}}$ run from $0$ up to some maximum at the points where the flat cone meets the surface $\Sigma$.

>>>>

This is now a simple volume integral but we need to find the boundaries of $\mathcal{X}_p$ to write down the integration limits. There are two parts to the boundary of the (solid) truncated cone: the \emph{base}, defined as $B_p:=\Sigma\cap J^-(p)$, and the \emph{top} defined as the set corresponding to the lightcone emanating at $p$ with all points below $\Sigma$ removed, written as $T_p:=\partial J^-(p)\cap J^+(\Sigma)$. Now the boundary of $\mathcal{X}_p$ is simply $\partial\mathcal{X}_p=B_p\cup T_p$. First we look at the top. Following \cite{Khetrapal_Sumati:Causal_Diamond_Volume} it can be shown that the first curvature correction to the lightcone volume comes in at $O (T^{d+2})$ and so can be ignored for our purposes. This means that the top can be treated effectively as a flat lightcone in RNCs, emanating from the point on the time axis at coordinate $T$, and thus it corresponds to the set of points satisfying $\sum_{i=1}^{d-1}\left(y^\ibar\right)^2= T-\overline{t}$ where the coordinates  $y^{\overline{i}}$ run from $0$ up to some maximum at the points where the flat cone meets the surface $\Sigma$.
